Initial Analysis

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Fixed all mf anoying country names

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(sf_eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                              ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                     ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                            ifelse(fishing_entity =="Italy","Italy",
                                                   ifelse(eez_name =="Chile (mainland)","Chile",
                                                          ifelse(fishing_entity =="Brazil","Brazil",
                                                                 ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                        ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                               ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                      ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
                                                                                             ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
                                                                                                    ifelse(eez_name =="Viet Nam","Vietnam",
                                                                                                           ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain (Mediterranean and Gulf of Cadiz)",
                                                                                                                         paste(eez_name)
                                                                                                                  )
                                                                                                           )
                                                                                                    )
                                                                                             ))))))))))
  ),	
  fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
  )
  )

@@

# matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>% 
#   mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
  clean_names()

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                         ifelse(fishing_entity =="Italy","Italy",
                                                ifelse(eez_name =="Chile (mainland)","Chile",
                                                       ifelse(fishing_entity =="Brazil","Brazil",
                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                   ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
                                                                                          ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
                                                                                          paste(eez_name)
                                                                                          )
                                                                                   )
                                                                            )
                                                       )))))))
                           ),
         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
         )
  )

# UN Regions dataset
UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  # mutate(un_fishing_entity = country_or_area) %>% 
  group_by(#un_fishing_entity,
           fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  ) %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Congo","Congo, R. of",
                            ifelse(fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
                            )
  ) %>% 
  filter(fishing_entity != "Solomon Isl." | sub_region != "Micronesia")

# Manually change congo
# UN_Regions[52,1] <- "Congo, R. of"

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name) %>% 
  mutate(
    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
    fishing_entity = gsub( "United States", "USA",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
  )

@@

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = "+proj=eck4")
  # st_transform(crs = 4326) # 4326

# World_sf %>% filter(str_detect(eez_name, "Cu"))

#### Determine polygon areas

# EEZ Area
EEZ_Area <- World_sf %>% 
  as.data.frame() %>% 
  group_by(eez_name) %>% 
  summarise(Size_EEZ = sum(Area_km2))

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity,OBJECTID) %>% 
  summarise(Size_Entity = sum(Area_km2))

# Regional EEZ area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  mutate(value = 1.16 * value)

@@

SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2005_09.csv", sep =""))

# Set global values for catch and revenue (within EEZ with re-constructed catch)
SAU_Global_Data <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
         )

# List of species
Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
                           ),
         fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
                                 ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",fishing_entity))
         )

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity,OBJECTID) %>% 
  summarise(Size_Entity = sum(Area_km2))

### Tnas and billfish according to Pons 2016

tunas <- c("Katsuwonus pelamis",
"Thunnus alalunga",
"Thunnus albacares",
"Thunnus maccoyii",
"Thunnus obesus",
"Thunnus orientalis", 
"Thunnus thynnus",
"Xiphias gladius",
"Istiophorus albicans",
"Istiophorus platypterus", 
"Istiompax indica",
"Makaira nigricans",
"Kajikia albidus",
"Kajikia audax",
"Tetrapturus angustirostris",
"Tetrapturus belone",
"Tetrapturus georgii",
"Tetrapturus pfluegeri")

@@

# number of eezs
length(unique(sau_eez_fes$eez_name))
# Number of coastal territories
length(unique(sau_eez_fes$fishing_entity))

@@

# Percentage of transboundary species from sampled
n_trans/938*100

@@

# Percentage catch of species analyzed from the identified species
Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.57%

# Percentage species analyzed from the identified species
Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.2%

@@

Summary_Trans <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

### New estimates!!!

# Filter SAU data for only those sampled species

SAU_Sampled_Data <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id,eez_name) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
  left_join(Exploited_Species) %>% 
  filter(!is.na(taxon_name)) %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

x <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  left_join(SAU_Sampled_Data,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>%
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100)

Summary_Trans <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

@@

Summary_Trans_vicky <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  left_join(SAU_Global_Vicky,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>%
  group_by() %>%
  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100);Summary_Trans_vicky

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  ) %>% 
  # bind_rows(Species_Left_Out) %>% 
  group_by(taxon_key,fishing_entity,eez_name) %>% 
  summarise(n()) %>% 
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","eez_name"))

@@

@@

  # Discrete species (not in Tresholded)
Discrete_Exclusive <- Clean_Results_Trans %>% 
  filter(!taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
  bind_rows(Species_Left_Out) %>% 
  group_by(taxon_key) %>% 
  summarise(n())

@@

>>>>

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(sf_eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                              ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                     ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                            ifelse(fishing_entity =="Italy","Italy",
                                                   ifelse(eez_name =="Chile (mainland)","Chile",
                                                          ifelse(fishing_entity =="Brazil","Brazil",
                                                                 ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                        ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                               ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                      ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
                                                                                             ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
                                                                                                    ifelse(eez_name =="Viet Nam","Vietnam",
                                                                                                           ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain",
                                                                                                                         paste(eez_name)
                                                                                                                  )
                                                                                                           )
                                                                                                    )
                                                                                             ))))))))))
  ),	
  fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
  )
  )

@@

matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>%
  mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))

# Spatial Data needed to remove duplicates
# sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
  # clean_names()

# New dara produced by Vicky 
sau_eez_fes <- read_excel("~/Desktop/EEZ_FishingEntityID_v2_9June2020.xlsx")

Clean_sau_eez_fes <- sau_eez_fes

# UN Regions dataset
UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  # mutate(un_fishing_entity = country_or_area) %>% 
  group_by(#un_fishing_entity,
    fishing_entity = country_or_area,
    georegion = region_name,
    sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("","",fishing_entity),
    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Mayotte","Mayotte (France)",fishing_entity),
    fishing_entity = gsub("Guadeloupe","Guadeloupe (France)",fishing_entity),
    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
    fishing_entity = gsub("Martinique","Martinique (France)",fishing_entity),
    fishing_entity = gsub("Montserrat","Montserrat (UK)",fishing_entity),
    fishing_entity = gsub("New Caledonia","New Caledonia (France)",fishing_entity),
    fishing_entity = gsub("Niue","Niue (New Zealand)",fishing_entity),
    fishing_entity = gsub("Norfolk Island","Norfolk Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
    fishing_entity = gsub("Pitcairn","Pitcairn (UK)",fishing_entity),
    fishing_entity = gsub("Puerto Rico","Puerto Rico (USA)",fishing_entity),
    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
    fishing_entity = gsub("Anguilla","Anguilla (UK)",fishing_entity),
    fishing_entity = gsub("Svalbard and Jan Mayen Islands","Svalbard Isl. (Norway)",fishing_entity),
    fishing_entity = gsub("Tokelau","Tokelau (New Zealand)",fishing_entity),
    fishing_entity = gsub("Turks & Caicos Islands","Turks & Caicos Isl. (UK)",fishing_entity),
    fishing_entity = gsub("United States Virgin Islands","US Virgin Isl.",fishing_entity),
    fishing_entity = gsub("Wallis and Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
    fishing_entity = gsub("Saint Barthélemy","St Barthelemy (France)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)","Iran",fishing_entity),
    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub("United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    # fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Congo","Congo, R. of",fishing_entity),
    # fishing_entity = gsub("Réunion","Réunion (France)",fishing_entity),
  ) %>%
  # Some of them do not work with gsub
  mutate(
    fishing_entity = ifelse(fishing_entity == "Venezuela (Bolivarian Republic of)","Venezuela",
                                 ifelse(fishing_entity == "Democratic Republic of the Congo, R. of","Congo (ex-Zaire)",
                                        ifelse(fishing_entity == "Iran (Islamic Republic of)","Iran",
                                               ifelse(fishing_entity == "Saint Martin (French Part)","St Martin",
                                                      ifelse(fishing_entity == "Cocos (Keeling) Islands","Cocos (Keeling) Isl. (Australia)",
                                                             ifelse(fishing_entity == "Falkland Islands (Malvinas)","Falkland Isl. (UK)",
                                                                    ifelse(fishing_entity =="Micronesia (Federated States of)","Micronesia",
                                                                           ifelse(fishing_entity == "Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",
                                                                                  ifelse(fishing_entity == "Sint Maarten (Dutch part)","Sint Maarten",
                                                                                         paste(fishing_entity)
  ) %>%
  filter(fishing_entity != "Solomon Isl." | sub_region != "Micronesia")

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name_long) %>% 
  mutate(
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
    fishing_entity = gsub("United States", "USA",fishing_entity),
    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
  )

@@

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name,
         eez_id = EEZID) %>% 
  st_transform(crs = "+proj=eck4") %>% 
  mutate(
    eez_id = ifelse(eez_name == "Russia (Laptev to Chukchi Sea)",913,eez_id)
  )

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  filter(!fishing_entity_id %in% c(213,223,207,208)) %>%  # Remove high seas and 207 and 208 that we do not know 
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  mutate(value = 1.16 * value)

@@

# Set global values for catch and revenue (within EEZ with re-constructed catch)
SAU_Global_Data <- SAU_Tim_Data %>%
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) #%>% 
  # mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
         # )

# List of species
# Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
  ),
  fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
                          ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",
                                 ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)","Spain",fishing_entity)))
  )

@@

# number of eezs
length(unique(World_sf$eez_name))

# Number of coastal territories
length(unique(sau_eez_fes$fishing_entity))

@@

# Percentage of transboundary species from sampled
n_trans/nrow(Species_Sampled)*100

@@

# Percentage catch of species analyzed from the identified species
Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.52%

# Percentage species analyzed from the identified species
Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.22%

@@

# Numbers for paper
Summary_Trans <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

@@

Summary_Trans_vicky <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  group_by(taxon_key,fishing_entity_id) %>% 
  summarise(n()) %>% 
  left_join(SAU_Global_Vicky,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>% # I think they used high seas data as well?
  group_by() %>%
  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100); Summary_Trans_vicky

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  ) %>% 
  group_by(taxon_key,fishing_entity,eez_name) %>% 
  summarise(n()) %>% 
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity"))

@@

Summary_Discrete <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  semi_join(Discrete,
            by = c("taxon_key","fishing_entity")
            ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Dis = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Dis/Total_Sampled*100,
         Per_SAU = Total_Dis/Total_Global*100)

@@

  # Discrete species (not in Tresholded)
Discrete_Exclusive <- Discrete %>% 
  filter(!taxon_key %in% Tresholded_T_Data$taxon_key) %>% 
  bind_rows(Species_Left_Out) %>%
  group_by(taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Exploited_Species)

@@

```{r test, eval = F, echo = F}

Tra <- Summary_Trans %>% 
  mutate(Type = "Trans")

Dis <- Summary_Discrete %>% 
  mutate(Type = "Dis")

Solo <- Summary_Discrete_Exclusive %>% 
  mutate(Type = "Solo")

All <- bind_rows(Tra,Dis,Solo) %>% 
  select(1:7) %>% 
  group_by(taxon_key,fishing_entity) %>% 
  summarise(n())

missing <- anti_join(Total_SAU_Sampled,All,
          by = c("fishing_entity_id","taxon_key"))

missing %>% 
  group_by(Variable) %>% 
  summarise(sum(Value))

# Now
58242635
# Goal
58986239
